---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# c212: Methods for Detecting Safety Signals in Clinical Trials Using Body-Systems (System Organ Classes) 

<!-- badges: start -->
<!-- badges: end -->

The goal of c212 is to provide provides a self-contained set of methods, which use groupings of adverse events, to aid clinical trial safety investigators, statisticians and researchers, in the early detection of adverse events.

## Installation

You can install the released version of c212 from [CRAN](https://CRAN.R-project.org) with:

``` r
install.packages("c212")
```

And the development version from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("rcarragh/c212")
```

## Example

This is a basic example which shows how to apply the Double False Discovery Rate to a set of multiple hypotheses:

```{r example1}
library(c212)
data(c212.FDR.data)
c212.err.cntrl(c212.FDR.data, method="DFDR", alpha = 0.05)
```

This is an example of how to apply the Berry and Berry model:

```{r example2}
library(c212)
data(c212.trial.data)
mod.BB <- c212.BB(c212.trial.data, burnin = 100, iter = 200)
```
